Simulation Figures for Genome Biology (simulations)

### 2018-06-26 manuscript_figures/manuscript_figures_sims.Rmd
Check sim plots w/ more pi0

methodset <- c("bonf", "bh", "ihw-a10", "qvalue", "bl-df03", "lfdr",
               "scott-empirical", "scott-theoretical", "ashq")
```

@@

## not including SE because it's too small
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

## not including SE because it's too small
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    ##geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

```{r, fig.width = 15, fig.height = 7.5}
plot_grid(pfdr + guides(color = FALSE, linetype = FALSE),
          ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])

## trimmed ranges
gp <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 15, height = 7.5)
```

>>>>

methodset <- c("bonf", "bh", paste0("ihw-a", round(alpha * 100)),
               "qvalue", "bl-df03", "lfdr",
               "scott-empirical", "scott-theoretical", "ashq")
```

@@

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

## including SE to show variability in FDRR
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

@@

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 15, height = 7.5)

## trimmed ranges
gp_zoom <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                     ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp_zoom

ggsave(file.path(outdir, "FigureSsim-nullprop-zoom.pdf"), gp_zoom, width = 15, height = 7.5)
```
